---
title: "TwitterNetworks"
author: "Yiqi Li"
date: "2/24/2022"
output: html_document
---
Important Google links:
https://docs.google.com/spreadsheets/d/1hKYBLE7YCXpmMWOKcjHUHnLdmmnOVfKwMY36_8PMG0Y/edit#gid=1519039184

https://docs.google.com/spreadsheets/d/1SgOANuyzLyxS9V5MZMWJPxqZXEeOIAAHwNSCFfLldRU/edit#gid=456669455

https://docs.google.com/spreadsheets/d/1OLSyfG94uZGGR_SCujWKJQDzGGUvlxktCOBM8A3w26M/edit#gid=1207703933 
12 new people

https://docs.google.com/spreadsheets/d/1H6y3PJcE-zh1Ing72Rq6q2ZRFmHPVoIC5U_6Cgl7I3Y/edit#gid=0
50people
Json: https://drive.google.com/drive/u/2/folders/14bsRuGizio89KCP5hkYdOiwqAt2B5XcY


```{r}
install.packages("stringr")
library(stringr)
```
#Read in files
```{r}
path="C:/Users/82419/OneDrive - Syracuse University/2021Fall/FAship/Twitter_R/TwitterNetworks/Excel Files of Tweets"
allfiles<-list.files(path=path, pattern= "_retweets.xlsx")
library(readxl)
retweet_data <- read_excel(paste(path,allfiles[1],sep = "/"))#change [1] to [2] [3] [4]... accordingly if you want to read in a separate user's file
max(as.Date(retweet_data$tweet_created_at))
min(as.Date(retweet_data$tweet_created_at))

#compare network changes using the granularity of "week"
Week <- as.Date(cut(as.Date(retweet_data$tweet_created_at), "week"))#week start on Monday

retweet_data$week<-Week
Keywords<-c('RT @')
retweet_data$receiver<-NA
for (i in (1: length(retweet_data$tweet_text))){
  receiver<-str_extract_all(retweet_data$tweet_text[i], "(?<=@)\\w+",simplify = FALSE)
  retweet_data$receiver[i]<-receiver
}
```
##Network size (excluding ego) for each week
```{r}
newdata<-data.frame()
uniqueweek<-unique(Week)
#creating edgelists for ego nets
for (i in (1:length(uniqueweek))){
  data<-subset(retweet_data,as.Date(retweet_data$week)==as.Date(uniqueweek[i]))
  alter<-c(unlist(data$receiver))
  edgelist<-cbind(tolower(retweet_data$username[1]),alter,as.character(uniqueweek[i]))
  newdata<-rbind(edgelist,newdata)
}
size<-vector()
for (i in (1:length(uniqueweek))){
  data<-subset(newdata,as.Date(newdata$V3)==as.Date(uniqueweek[i]))
  size<-append(size,nrow(data[!(tolower(retweet_data$username[1])%in%tolower(data$alter))]))
}
size_month<-as.data.frame(cbind(size,as.character(uniqueweek)))
size_month$V2 <- as.Date(size_month$V2)
plot(size_month$V2,size_month$size,type="o")
```
##Total number of unique users interacted for each unique week
```{r}
uniquesize<-vector()
for (i in (1:length(uniqueweek))){
  data<-subset(newdata,as.Date(newdata$V3)==as.Date(uniqueweek[i]))
  if(tolower(retweet_data$username[1])%in%tolower(data$alter)){#remove loops
    uniquesize<-append(uniquesize,length(unique(data$alter))-1)
}else{
    uniquesize<-append(uniquesize,length(unique(data$alter)))
  }
}
uniquesize_month<-as.data.frame(cbind(uniquesize,as.character(uniqueweek)))
uniquesize_month$V2 <- as.Date(uniquesize_month$V2)
plot(uniquesize_month$V2,uniquesize_month$uniquesize,type="o")#similar pattern
```
##The number of new alters user starts to interact each unique week
```{r}
newaltersize<-vector()
for (i in (1:length(uniqueweek))){
  data<-subset(newdata,as.Date(newdata$V3)==as.Date(uniqueweek[i]))
  previousdata<-subset(newdata,as.Date(newdata$V3)<as.Date(uniqueweek[i]))
  alter<-unique(data$alter)
  alter<-alter[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alter)))]
  oldalter<-unique(previousdata$alter)
  oldalter<-oldalter[!grepl(tolower(retweet_data$username[1]),unlist(tolower(oldalter)))]
  newaltersize<-append(newaltersize,length(unique(alter[!(alter %in% oldalter)])))
}
newaltersize
newaltersize_month<-as.data.frame(cbind(newaltersize,as.character(uniqueweek)))
newaltersize_month$V2 <- as.Date(newaltersize_month$V2)
plot(newaltersize_month$V2,newaltersize_month$newaltersize,type="o")
````

##Unique network size (excluding ego) for a weekly (can change to monthly by changing 6 to 29) sliding window with the granularity of "slider = n" day
```{r}
datelist<-seq(min(as.Date(retweet_data$tweet_created_at)), max(as.Date(retweet_data$tweet_created_at)), by="days")
i = 1
slider = 3 #sliding by 3 days. 
uniquesize<-vector()
date<-vector()

while ((i + 6 + slider) < length(datelist)){
  starting_date<-datelist[i]
  stop_date<-starting_date+6
  data<-subset(retweet_data,as.Date(retweet_data$tweet_created_at)>=starting_date)
  data<-subset(data,as.Date(data$tweet_created_at)<=stop_date)
  alter<-c(unlist(data$receiver))
  alter<-alter[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alter)))]
  date<-append(date,as.character(starting_date))
  uniquesize<-append(uniquesize,length(unique(alter)))
  i = i + slider
}

plot(as.Date(date),uniquesize,type="o")
```
##Unweighted jaccard similarity for a weekly (can change to monthly by changing 6 to 29) sliding window with the granularity of "slider = n" day
```{r}
jaccard <- function(a, b) {
    intersection = length(intersect(a, b))
    union = length(a) + length(b) - intersection
    return (intersection/union)
}

datelist<-seq(min(as.Date(retweet_data$tweet_created_at)), max(as.Date(retweet_data$tweet_created_at)), by="days")
i = 1
slider = 7  
jaccard_vector<-vector()
date<-vector()

while ((i + 6 + slider) < length(datelist)){
  starting_datei<-datelist[i]
  stop_datei<-datelist[i+6]
  datai<-subset(retweet_data,as.Date(retweet_data$tweet_created_at)>=starting_datei)
  datai<-subset(datai,as.Date(datai$tweet_created_at)<=stop_datei)
  alteri<-c(unlist(datai$receiver))
  alteri<-alteri[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alteri)))]
  starting_datej<-datelist[i+slider]
  stop_datej<-datelist[i+slider+6]
  dataj<-subset(retweet_data,as.Date(retweet_data$tweet_created_at)>=starting_datej)
  dataj<-subset(dataj,as.Date(dataj$tweet_created_at)<=stop_datej)
  alterj<-c(unlist(dataj$receiver))
  alterj<-alterj[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alterj)))]
  allalter<-unique(append(alteri,alterj))
  v1<-vector()
  if(length(allalter)>0){#if both vectors are empty,no need to calculate jaccard similarity. datapoint will also be empty
    for (k in (1:length(allalter))){
      if(allalter[k]%in%alteri){
        v1<-append(v1,1)
      }else{
        v1<-append(v1,0)
      }
    }
    v2<-vector()
    for (k in (1:length(allalter))){
      if(allalter[k]%in%alterj){
        v2<-append(v2,1)
      }else{
        v2<-append(v2,0)
      }
    }
    jaccard_vector<-append(jaccard_vector,jaccard(v1,v2))
    date<-append(date,as.character(starting_datei))
  }
  i = i + slider
}

plot(as.Date(date),jaccard_vector,type="o")

```

##unweighted jaccard similarity for each unique week

```{r}
uniqueweek<-unique(newdata$V3)
jaccard_vector<-vector()
date<-vector()
for (i in (2:length(uniqueweek))){
  datai<-subset(newdata,as.Date(newdata$V3)==as.Date(uniqueweek[i]))
  alteri<-c(unlist(datai$alter))
  alteri<-alteri[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alteri)))]
  j<-i-1
  dataj<-subset(newdata,as.Date(newdata$V3)==as.Date(uniqueweek[j]))
  alterj<-c(unlist(dataj$alter))
  alterj<-alterj[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alterj)))]
  allalter<-unique(append(alteri,alterj))
  v1<-vector()
  if(length(allalter)>0){#if both vectors are empty,no need to calculate jaccard similarity. datapoint will also be empty
    for (k in (1:length(allalter))){
      if(allalter[k]%in%alteri){
        v1<-append(v1,1)
      }else{
        v1<-append(v1,0)
      }

    v2<-vector()
    for (k in (1:length(allalter))){
      if(allalter[k]%in%alterj){
        v2<-append(v2,1)
      }else{
        v2<-append(v2,0)
      }
    }
    jaccard_vector<-append(jaccard_vector,jaccard(v1,v2))
    date<-append(date,as.character(uniqueweek[i]))
  }

  }
}

plot(as.Date(date),jaccard_vector,type="o")

```
##Sliding Window Weighted Jaccard Similarity for a weekly (can change to monthly by changing 6 to 29) sliding window with the granularity of "slider = n" day
```{r}
jaccard_w <- function(a, b) {
    num <- sum(sapply(1:length(a), function(i)(min(a[i],b[i]))))
    den <- sum(sapply(1:length(a), function(i)(max(a[i],b[i]))))
    return (num/den)
}
datelist<-seq(min(as.Date(retweet_data$tweet_created_at)), max(as.Date(retweet_data$tweet_created_at)), by="days")
i = 1
slider = 5 #sliding by 3 days. 
jaccard_vector<-vector()
date<-vector()

while ((i + 6 + slider) < length(datelist)){
  starting_datei<-datelist[i]
  end_datei<-datelist[i + 6]
  starting_datej<-datelist[i + slider]
  end_datej<-datelist[i + 6 + slider]
  datai<-subset(retweet_data,as.Date(retweet_data$tweet_created_at)>=starting_datej)
  datai<-subset(datai,as.Date(datai$tweet_created_at)<=end_datei)
  alteri<-c(unlist(datai$receiver))
  alteri<-alteri[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alteri)))]
  
  dataj<-subset(retweet_data,as.Date(retweet_data$tweet_created_at)>=starting_datej)
  dataj<-subset(dataj,as.Date(dataj$tweet_created_at)<=end_datej)
  alterj<-c(unlist(dataj$receiver))
  alterj<-alterj[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alterj)))]
  allalter<-unique(append(alteri,alterj))
  if(length((allalter))>0){
    v1<-vector()
    v2<-vector()
    for (k in (1:length(allalter))){
      if(allalter[k]%in%alteri){
        v1<-append(v1,length(alteri[alteri==allalter[k]]))
      }else{
        v1<-append(v1,0)
      }
    }
    for (k in (1:length(allalter))){
      if(allalter[k]%in%alterj){
        v2<-append(v2,length(alterj[alterj==allalter[k]]))
      }else{
        v2<-append(v2,0)
      }
    }
  }
  jaccard_vector<-append(jaccard_vector,jaccard_w(v1,v2))
  date<-append(date,as.character(starting_datei))
  i = i + slider
  print(i)
}
plot(as.Date(date),jaccard_vector,type="o")
```
https://www.sg.ethz.ch/publications/2019/zingg2019what-is-the/entropy-21-00901.pdf
From Josh:
"entropy is kind of of proxy for diversity.  You could use it to measure the diversity of a person’s ego network over each time window.  Like this:

Consider user A in time window 1.  User A mentions (or retweets, or whatever) four others users a certain number of times:

B = 10
C = 10
D = 10
E = 50

Then in window 2, user A mentions (or retweets) four others, like this:

J = 5
K = 5
L = 10
M = 20

Note that we don’t care who is being mentioned.  We’re just looking at the raw counts.

Entropy is is just -sum(p*log2(p)) over all users. So,

Window 1:  - [(.125 * -3) + (.125 * -3) +  (.125 * -3)+ (.5*-.678)] = 1.464
Window 2:  -[(.125 * -3) + (.125 * -3) + (.25 * -2) + (.5*-1)] = 1.75

This means that the diversity (i.e. randomness) of the users communication pattern is going up.  Note that for four alters, maximum entropy would be:

 - [(.25*-2)+(.25*-2)+(.25*-2)+(.25*-2)] = 2

Which means complete randomness or maximum diversity for this number of alters."

##Entropy in unique week
```{r}
uniqueweek<-unique(newdata$V3)
entropy_vector<-vector()
date<-vector()
for (i in (1:length(uniqueweek))){
  data<-subset(newdata,as.Date(newdata$V3)==as.Date(uniqueweek[i]))
  alter<-c(unlist(data$alter))
  alter<-alter[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alter)))]
  if(length(alter)>0){
     freq_table<-as.data.frame(table(alter))
    entropy<-(-sum(sapply(1:length(freq_table$a),function(x)((freq_table$Freq[x]/sum(freq_table$Freq))*log2(freq_table$Freq[x]/sum(freq_table$Freq))))))
    entropy_vector<-append(entropy_vector,entropy)
    date<-append(date,as.character(uniqueweek[i]))
  }
 
}
plot(as.Date(date),entropy_vector,type="o")
```
##Entropy in a sliding weekly window

```{r}
datelist<-seq(min(as.Date(retweet_data$tweet_created_at)), max(as.Date(retweet_data$tweet_created_at)), by="days")
i = 1
slider = 5 
entropy_vector<-vector()
date<-vector()

while ((i + 6 + slider) < length(datelist)){
  starting_datei<-datelist[i]
  stop_datei<-datelist[i]+6
  datai<-subset(retweet_data,as.Date(retweet_data$tweet_created_at)>=starting_datei)
  datai<-subset(datai,as.Date(datai$tweet_created_at)<=stop_datei)
  alter<-c(unlist(datai$receiver))
  alter<-alter[!grepl(tolower(retweet_data$username[1]),unlist(tolower(alter)))]#this line was wrong, now is fixed
  if(length(alter)>0){
    freq_table<-as.data.frame(table(alter))
    entropy<-(-sum(sapply(1:length(freq_table$a),function(x)((freq_table$Freq[x]/sum(freq_table$Freq))*log2(freq_table$Freq[x]/sum(freq_table$Freq))))))
    entropy_vector<-append(entropy_vector,entropy)
    date<-append(date,as.character(starting_datei))
  }
  i = i + slider
}


plot(as.Date(date),entropy_vector,type="o")
```

Another alternative method maybe we could try: https://www.emerald.com/insight/content/doi/10.1108/MD-05-2019-0597/full/html#sec003
Ego-network stability reflects the extent to which the composition of the focal organization's ego network remains unchanged from one period to the next (Kumar and Zaheer, 2019). 